### 2022-03-20 CV2/CV.tex
cv

\section{Research Interests}
 Optimization Algorithms, Distributed Optimization, Machine Learning,

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET\\
	\textsc{Computer} & macOS, LaTeX, Git\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
\end{tabular}

@@

\section{Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{tabular}{cl}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabular}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

@@

\section{Papers}

>>>>

\section{Research Interests}
Optimization Algorithms, Distributed Optimization, Machine Learning
%\begin{tabular}{cl}
%\qquad\qquad\qquad&  Optimization Algorithms\\
%&  Distributed Optimization\\
%&  Machine Learning
%\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
	\textsc{Computer} & macOS, LaTeX, Git\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
\end{tabular}

@@

\section{Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{tabular}{cl}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
	\textsc{2018} & {\bf Dean's Award}, King Abdullah University of Science and Technology\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabular}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

@@

### 2022-03-20 CV2/papers.tex
cv

@@

\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint}
\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint}
\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint}

@@

\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.11079}{\em \color{black}arXiv preprint}

@@

\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.08374}{\em \color{black}arXiv preprint}
\item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint}

@@

\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint}

@@

\item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M. Gower}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}), \href{https://arxiv.org/abs/2002.11337}{\em \color{black}arXiv preprint}

@@

\item \textbf{Distributed Fixed Point Methods with Compressed Iterates} (\href{https://scholar.google.com/citations?user=gyiubRkAAAAJ}{\color{linkcolour}Selim Chraibi}, \href{https://rka97.github.io}{\color{linkcolour}Ahmed Khaled}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}), \href{https://arxiv.org/abs/1912.09925}{\em \color{black}arXiv preprint}
\item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint}

@@

\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U. Stich}), \href{https://arxiv.org/abs/1904.05115}{\em \color{black}arXiv preprint}

@@

>>>>

\section{{Publications}}

@@

@@

@@

@@

@@

@@

@@

@@

\newpage
\section{{Preprints}}
\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint (February 2022)}
\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint (December 2021)}
\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint (July 2021)}
\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.11079}{\em \color{black}arXiv preprint (February 2021)}
\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.08374}{\em \color{black}arXiv preprint (February 2021)}
\item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}
\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint (September 2020)}
\item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M. Gower}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}), \href{https://arxiv.org/abs/2002.11337}{\em \color{black}arXiv preprint (February 2020)}
\item \textbf{Distributed Fixed Point Methods with Compressed Iterates} (\href{https://scholar.google.com/citations?user=gyiubRkAAAAJ}{\color{linkcolour}Selim Chraibi}, \href{https://rka97.github.io}{\color{linkcolour}Ahmed Khaled}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}), \href{https://arxiv.org/abs/1912.09925}{\em \color{black}arXiv preprint (December 2019)}
\item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint (December 2019)}
\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U. Stich}), \href{https://arxiv.org/abs/1904.05115}{\em \color{black}arXiv preprint (April 2019)}
\bigskip
\begin{center}
Last Updated on March 20, 2022
\end{center}
